Continuous Generalization of Buildings

### 2017-08-07 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the implementation of a basic version of growing buildings

@@

If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
grow at most $2d_\mathrm{G}$.
The length of a bridge can be as large as
\begin{equation}
\label{eq:BridgeLength}
l_b=4d_\mathrm{G}+d_\epsilon.
\end{equation}
\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}

@@

@@

>>>>

$\bar{a}$

@@

If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
grow at most $2d_\mathrm{G}$.
The length of a bridge can be as large as
\begin{equation}
\label{eq:BridgeLength}
l_b=4d_\mathrm{G}+d_\epsilon.
\end{equation}
%\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that Imai--Iri simplification 
algorithm \parencite{ImaiIri1988} fit our needs well.

@@

The closest place of two buildings before enlarging is not necessarily the same 
as the closest place after enlarging.
